
```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Part 2: R Markdown for gapminder data exploration

This will detail some basic functions for extracting and visualizing information from the given dataframe: gapminder. There is a document titled hw01-gapminder.docx that incorporates the visual output of all the methods used below. 

### Inputing the gapminder dataframe

Use the following command to access the gapminder dataframe in your working environment

```{r,gapminder, echo=TRUE}

library(gapminder)
```

### Extracting information about the dataframe 

##### Viewing the header

Use this command to view the first six observations of this dataframe

```{r, echo=TRUE}
head(gapminder)
```

##### Viewing the dataframe type

The structure function will yield all the variable types

```{r, echo=TRUE}
str(gapminder)
```
#### Retrieving a summary of the dataframe

The summary function will provide a brief summary of the data frame type and its varibles and observations

```{r, echo=TRUE}
summary(gapminder)
```

### Visualizing data from the dataframe

Here is a scatterplot of life expectancies of countries in different continents

```{r, echo=TRUE}
library(tidyverse)
ggplot(data=gapminder)+geom_point(mapping = aes(x=continent, y=lifeExp))
```


